Solving Collective Spin Hamiltonians with Decoherence

### 2018-08-21 soc_squeezing/cumulant_expansions.tex
finished commutator derivation

This text makes ubiquitous use of various spin operator identities; we
collect and derive particularly useful identities here for reference.
The elementary commutation relations between single-weight spin
operators are
\begin{align}
  \f12 \sp{\sigma_j^z,\sigma_k^\mu}_-
  &= \delta_{jk} \mu \sigma_j^\mu,
  &
  \sp{S_z,\sigma_j^\mu}_-
  &= \f12 \sp{\sigma_j^z,S_\mu}_- = \mu \sigma_j^\mu,
  &
  \sp{S_z,S_\mu}_-
  &= \mu S_\mu,
  \label{eq:comm_z_mu} \\
  \sp{\sigma_j^\mu,\sigma_k^\nu}_-
  &= \delta_{jk} \delta_{\mu,-\nu} \mu \sigma_j^z,
  &
  \sp{S_\mu,\sigma_j^\nu}_-
  &= \sp{\sigma_j^\mu,S_\nu}_-
  = \delta_{\mu,-\nu} \mu \sigma_j^z,
  &
  \sp{S_\mu,S_\nu}_-
  &= \delta_{\mu,-\nu} 2 \mu S_z.
  \label{eq:comm_mu_nu}
\end{align}
These relations can be used to inductively determine commutation
relations between higher-weight spin operators.  In particular, we can
find that
\begin{align}
  S_z S_\mu^m
  = \p{\mu S_\mu + S_\mu S_z} S_\mu^{m-1}
  = \mu S_\mu^m + S_\mu S_z S_\mu^{m-1}
  = 2 \mu S_\mu^m + S_\mu S_z S_\mu^{m-2}
  = S_\mu^m \p{\mu m + S_z},
  \label{eq:push_z_mu}
\end{align}
and in turn
\begin{align}
  S_z S_\mu^m S_\nu^n
  = S_\mu^m \p{\mu m + S_z} S_\nu^n
  = S_\mu^m S_\nu^n \p{\mu m + \nu n + S_z}.
  \label{eq:push_z_mu_nu}
\end{align}
Repeating this process $\ell$ times tells us
\begin{align}
  S_z^\ell S_\mu^m S_\nu^n
  = S_\mu^m S_\nu^n \p{\mu m + \nu n + S_z}^\ell,
\end{align}
which implies
\begin{align}
  \sp{S_z^\ell, S_\mu^m S_\nu^n}_-
  = S_\mu^m S_\nu^n \p{\sp{\mu m + \nu n + S_z}^\ell - S_z^\ell}
  = S_\mu^m S_\nu^n  \sum_{k=0}^{\ell-1} {\ell \choose k}
  \p{\mu m + \nu n}^{\ell-k} S_z^k.
  \label{eq:comm_z_mu_nu_pow}
\end{align}

\section{Commutators between high-weight transverse spin operators}

@@

track of high-weight operators which are linearly independent.  We

@@

  recursive} expression for $C_{\mu mn}$, and we have not even managed
to order the spin operators, as $C_{\mu,m-k-1,n-1}$ contains $S_z$
operators which are to the left of $S_\mu^k$.  To sort all spin
operators once and for all, we define

@@

While the resulting expression strongly resembles that in
\eqref{eq:C_mn}, there is one crucial difference: all spin operators
in \eqref{eq:C_mn_k} have been ordered.  We can now repeatedly
substitute $C_{\mu mn}^{(k)}$ into itself, each time decreasing $m$
and $n$ by 1, until one of $m$ or $n$ reaches zero.  Such repeated
substitution yields the expansion

@@

\eqref{eq:C_mn_E}-\eqref{eq:E_mn_p} provide a well-defined expansion
for the commutator $\sp{S_\mu^m,S_\nu^n}_- = C_{\mu mn}$, but the
expression for $E_{\mu mn}^{(p)}$ in \eqref{eq:E_mn_p} is -- put it
lightly -- quite a mess, involving a sum over $p$ mutually related
intermediate variables!  We therefore devote the rest of this section
to simplifying $E_{\mu mn}^{(p)}$.

Observing that we always have $k_1\le k_2\le\cdots\le k_p$, we can
reverse the order of the sums in \eqref{eq:E_mn_p} and re-index
$k_p\to\ell$ to get
\begin{align}
  E_{\mu mn}^{(p)}
  = \f{n!}{\p{n-p}!}
  \sum_{\ell=0}^{m-p-1} D_{\mu,m-p,n-p}^{(\ell)} \p{2\ell+p-n+2\mu S_z}
  \sum_{\substack{\v k\in\Z_{\ell+1}^{p-1}\\k_{p-1}\ge\cdots\ge k_1}}
  \prod_{j=1}^{p-1} \p{2k_j+j-n+2\mu S_z},
\end{align}
where $\Z_q$ denotes the set of $q$ smallest non-negative integers,
e.g.~$\Z_{\ell+1}=\set{0,1,\cdots,\ell}$.  Defining for shorthand
\begin{align}
  \sum_{\p{\v k,p,\ell}} X \equiv
  \sum_{\substack{\v k\in\Z_{\ell+1}^{p-1}\\k_{p-1}\ge\cdots\ge k_1}} X,
  &&
  F_{\mu np} \equiv p - n + 2\mu S_z,
\end{align}
we can say
\begin{align}
  E_{\mu mn}^{(p)}
  = \f{n!}{\p{n-p}!}
  \sum_{\ell=0}^{m-p-1} D_{\mu,m-p,n-p}^{(\ell)} \p{2\ell+F_{\mu np}}
  \sum_{\p{\v k,p,\ell}} \prod_{j=1}^{p-1} \p{2k_{p-j}-j+F_{\mu np}}.
  \label{eq:E_mn_p_k_sum}
\end{align}
We now define
\begin{align}
  f_{\mu np\ell}\p{k,q} \equiv \p{\ell-k+q} \p{\ell+k-q+F_{\mu np}},
\end{align}
and evaluate sums successively over $k_{p-1},k_{p-2},\cdots,k_2,k_1$
respectively from $k_{p-2},k_{p-3},\cdots,k_1,0$ to $\ell$, finding
\begin{align}
  \sum_{\p{\v k,p,\ell}} \prod_{j=1}^{p-1} \p{2k_{p-j}-j+F_{\mu np}}
  &= \sum_{\p{\v k;p-1;\ell}}
  \prod_{j=2}^{p-1} \p{2k_{p-j}-j+F_{\mu np}}
  f_{\mu n\ell}\p{k_{p-2},1} \\
  &= \f12 \sum_{\p{\v k,p-2,\ell}}
  \prod_{j=3}^{p-1} \p{2k_{p-j}-j+F_{\mu np}}
  f_{\mu np\ell}\p{k_{p-3},1} f_{\mu np\ell}\p{k_{p-3},2} \\
  &= \f1{r!} \sum_{\p{\v k,p-r,\ell}}
  \prod_{j=1+r}^{p-1} \p{2k_{p-j}-j+F_{\mu np}}
  \prod_{q=1}^r f_{\mu np\ell}\p{k_{p-1-r},q} \\
  &= \f1{\p{p-1}!} \prod_{q=1}^{p-1} f_{\mu np\ell}\p{0,q} \\
  &= { \ell + p - 1 \choose p - 1 }
  \prod_{q=1}^{p-1} \p{\ell-q+F_{\mu np}}.
\end{align}
Substitution of this result together with $D_{\mu,m-p,n-p}^{(\ell)}$
as given in using \eqref{eq:D_mn_k} into $E_{\mu mn}^{(p)}$ as
expressed in \eqref{eq:E_mn_p_k_sum} then gives us
\begin{align}
  E_{\mu mn}^{(p)}
  = \f{n!}{\p{n-p-1}!} S_\bmu^{n-p-1} S_\mu^{m-p-1} G_{\mu mnp}
  \label{eq:E_mn_p_G}
\end{align}
with
\begin{align}
  G_{\mu mnp}
  \equiv
  \sum_{\ell=0}^{m-p-1} { \ell + p - 1 \choose p - 1 }
  \p{m-p-\ell} \p{\ell+m-p+F_{\mu np}}
  \p{2\ell + F_{\mu np}}
  \prod_{q=1}^{p-1} \p{\ell-q+F_{\mu np}}.
\end{align}

% \vspace{3cm}

% With reference to \eqref{eq:E_mn_p_G}, we finally have
% \begin{align}
%   \sp{S_\mu^m, S_\bmu^n}_-
%   = C_{\mu mn}
%   = mn S_\bmu^{n-1} S_\mu^{m-1}
%   \sum_{q\in\set{0,1}} \p{m-n}^{1-q}\p{2\mu S_z}^q
%   + \sum_{p=1}^{\min\set{m,n}-1} E_{\mu mn}^{(p)}.
% \end{align}

% \begin{align}
%   \prod_{j=1}^{p-1} \p{2k_j+j-n+2\mu S_z}
%   = \sum_{q=0}^{p-1} \p{2\mu S_z}^q
%   \sum_{c\in\C_{p-1-q}\p{\Z_{p-1}}} \prod_{j\in c} \p{2k_{j+1}+j+1-n},
%   \label{eq:product_expansion}
% \end{align}
% where $\C\p{k,\S}$ denotes the set of $k$-combinations (i.e.~subsets
% with $k$ elements) of $\S$; the number of elements in
% $\C_{p-1-q}\p{\Z_{p-1}}$ is
% ${ p-1 \choose p-1-q } = { p-1 \choose q }$.

\vspace{3cm}

To derive a system of equations for the two-axis twisting Hamiltonian
we need to know $\sp{S_\mu^2,S_\bmu^n}_-$, so we expand
\begin{align}
  \sp{S_\mu^2,S_\bmu^n}_-
  = C_{\mu mn}
  = D_{\mu,2,n} + n D_{\mu,1,n-1} \p{1 - n + 2\mu S_z}
\end{align}

\newpage

\section{Decoherence of Heisenberg spin operators}
\label{sec:decoherence}

The decoherence operator for uncorrelated single-spin decay at a
uniform rate is
\begin{align}
  \D\p{\O}
  \equiv \sum_j\p{\sigma_j^+\O\sigma_j^-
    - \f12\sp{\sigma_j^+\sigma_j^-,\O}_+},
\end{align}
where
\begin{align}
  \sum_j \f12\sp{\sigma_j^+\sigma_j^-,\O}_+
  = \f12\sp{S+S_z,\O}_+
  = S\O + \f12\sp{S_z,\O}_+
  = \O\p{S+S_z} + \f12\sp{S_z,\O}_-,
\end{align}
so
\begin{align}
  \D\p{\O}
  = \sum_j \sigma_j^+\O\sigma_j^- - \O\p{S + S_z} - \f12 \sp{S_z,\O}_-.
\end{align}
We are interested in the effect of this decoherence on the dynamics of
collective spin operators, all of which are determined by operators of
the form $S_+^\ell S_-^m S_z^n$.  We thus expand
\begin{align}
  \D\p{S_+^\ell S_-^m S_z^n}
  = \sum_j \sigma_j^+ S_+^\ell S_-^m S_z^n \sigma_j^-
  - S_+^\ell S_-^m S_z^n \p{S + S_z}
  - \f12 \sp{S_z, S_+^\ell S_-^m S_z^n}_-.
  \label{eq:D_z+-}
\end{align}
The last term in \eqref{eq:D_z+-} is straightforward to simplify using
\eqref{eq:push_z_mu_nu}:
\begin{align}
  \f12 \sp{S_z, S_+^\ell S_-^m S_z^n}_-
  = \f12 \sp{S_z, S_+^\ell S_-^m}_- S_z^n
  = \f12 \p{\ell-m} S_+^\ell S_-^m S_z^n,
\end{align}
while the first term in \eqref{eq:D_z+-} can be written in terms of
collective spin operators if we use
\eqref{eq:comm_z_mu}-\eqref{eq:comm_mu_nu} to push the jump operators
together:
\begin{align}
  \sum_j \sigma_j^+ S_+^\ell S_-^m S_z^n \sigma_j^-
  = \sum_j S_+^\ell \sigma_j^+ \sigma_j^- S_-^m \p{S_z-1}^n
  = S_+^\ell \p{S + S_z} S_-^m
  \sum_{k=0}^n \p{-1}^{n-k} { n \choose k } S_z^k.
\end{align}
Finally, we need to push the middle $S_z$ to the right, which we can
do using \eqref{eq:push_z_mu}:
\begin{align}
  \sum_j \sigma_j^+ S_+^\ell S_-^m S_z^n \sigma_j^-
  = S_+^\ell S_-^m \p{S - m + S_z}
  \sum_{k=0}^n \p{-1}^{n-k} { n \choose k } S_z^k.
\end{align}
Putting everything together, we have that
\begin{align}
  \D\p{S_+^\ell S_-^m S_z^n}
  &= S_+^\ell S_-^m \sp{\p{S - m + S_z} \sum_{k=0}^n
    \p{-1}^{n-k} { n \choose k } S_z^k
    - \p{S + S_z + \f12\sp{\ell-m}} S_z^n} \\
  &= S_+^\ell S_-^m \sp{\p{S - m + S_z} \sum_{k=0}^{n-1}
    \p{-1}^{n-k} { n \choose k } S_z^k - \f12 \p{\ell+m} S_z^n}.
\end{align}

>>>>

This text makes ubiquitous use of various spin operator identities; we
collect and derive particularly useful identities here for reference.
The elementary commutation relations between single-weight spin
operators are
\begin{align}
  \f12 \sp{\sigma_j^z,\sigma_k^\mu}_-
  &= \delta_{jk} \mu \sigma_j^\mu,
  &
  \sp{S_z,\sigma_j^\mu}_-
  &= \f12 \sp{\sigma_j^z,S_\mu}_- = \mu \sigma_j^\mu,
  &
  \sp{S_z,S_\mu}_-
  &= \mu S_\mu,
  \label{eq:comm_z_mu} \\
  \sp{\sigma_j^\mu,\sigma_k^\nu}_-
  &= \delta_{jk} \delta_{\mu,-\nu} \mu \sigma_j^z,
  &
  \sp{S_\mu,\sigma_j^\nu}_-
  &= \sp{\sigma_j^\mu,S_\nu}_-
  = \delta_{\mu,-\nu} \mu \sigma_j^z,
  &
  \sp{S_\mu,S_\nu}_-
  &= \delta_{\mu,-\nu} 2 \mu S_z.
  \label{eq:comm_mu_nu}
\end{align}
These relations can be used to inductively determine commutation
relations between higher-weight spin operators.  In particular, we can
find that
\begin{align}
  S_z S_\mu^m
  = \p{\mu S_\mu + S_\mu S_z} S_\mu^{m-1}
  = \mu S_\mu^m + S_\mu S_z S_\mu^{m-1}
  = 2 \mu S_\mu^m + S_\mu S_z S_\mu^{m-2}
  = S_\mu^m \p{\mu m + S_z},
  \label{eq:push_z_mu}
\end{align}
and in turn
\begin{align}
  S_z S_\mu^m S_\nu^n
  = S_\mu^m \p{\mu m + S_z} S_\nu^n
  = S_\mu^m S_\nu^n \p{\mu m + \nu n + S_z}.
  \label{eq:push_z_mu_nu}
\end{align}
Repeating this process $\ell$ times tells us
\begin{align}
  S_z^\ell S_\mu^m S_\nu^n
  = S_\mu^m S_\nu^n \p{\mu m + \nu n + S_z}^\ell,
\end{align}
which implies
\begin{align}
  \sp{S_z^\ell, S_\mu^m S_\nu^n}_-
  = S_\mu^m S_\nu^n \p{\sp{\mu m + \nu n + S_z}^\ell - S_z^\ell}
  = S_\mu^m S_\nu^n  \sum_{k=0}^{\ell-1} {\ell \choose k}
  \p{\mu m + \nu n}^{\ell-k} S_z^k.
  \label{eq:comm_z_mu_nu_pow}
\end{align}
Similarly finding commutation relations between high-weight transverse
spin operators, i.e.~$S_\mu^m$ and $S_\nu^n$, turns out to be
considerably more difficult than the cases we have worked out thus
far.  We therefore save this case for Appendix
\ref{sec:comm_transverse}.

\newpage
\section{Commutators between high-weight transverse spin operators}
\label{sec:comm_transverse}

@@

track of high-weight operators that are linearly independent.  We

@@

  recursive} expression for $C_{\mu mn}$.  Furthermore, we have not
even managed to order the spin operators, as $C_{\mu,m-k-1,n-1}$
contains $S_z$ operators which are to the left of $S_\mu^k$.  To sort
all spin operators once and for all, we define

@@

While the resulting expression in \eqref{eq:C_mn_k} strongly resembles
that in \eqref{eq:C_mn}, there is one crucial difference: all spin
operators in \eqref{eq:C_mn_k} have been sorted into a standard order.
We can now repeatedly substitute $C_{\mu mn}^{(k)}$ into itself, each
time decreasing $m$ and $n$ by 1, until one of $m$ or $n$ reaches
zero.  Such repeated substitution yields the expansion

@@

\eqref{eq:C_mn_E}-\eqref{eq:E_mn_p} provide a complete expansion for
the commutator $\sp{S_\mu^m,S_\nu^n}_- = C_{\mu mn}$, but the result
is -- to put it lightly -- quite a mess: the expression for
$E_{\mu mp}^{(p)}$ in \eqref{eq:E_mn_p} involves a sum over $p$
mutually dependent intermediate variables!  We therefore devote the
rest of this section to simplifying our result for the commutator
$\sp{S_\mu^m,S_\nu^n}_-$.

Observing that we always have $k_1\le k_2\le\cdots\le k_p$, we can
reverse the order of the sums in \eqref{eq:E_mn_p} and relabel
$k_p\to\ell$ to get
\begin{align}
  E_{\mu mn}^{(p)}
  = \f{n!}{\p{n-p}!}
  \sum_{\ell=0}^{m-p-1} D_{\mu,m-p,n-p}^{(\ell)} \p{2\ell+p-n+2\mu S_z}
  \sum_{\substack{\v k\in\Z_{\ell+1}^{p-1}\\
      k_{p-2}\ge k_{p-1}\ge\cdots\ge k_1}}
  \prod_{j=1}^{p-1} \p{2k_j+j-n+2\mu S_z},
\end{align}
where $\Z_q$ denotes the set of $q$ smallest non-negative integers,
e.g.~$\Z_{\ell+1}=\set{0,1,\cdots,\ell}$.  Defining for shorthand
\begin{align}
  \sum_{\p{\v k,p,\ell}} X \equiv
  \sum_{\substack{\v k\in\Z_{\ell+1}^{p-1}\\
      k_{p-1}\ge k_{p-2}\ge\cdots\ge k_1}} X,
  &&
  F_{\mu np} \equiv p - n + 2\mu S_z,
\end{align}
we can say
\begin{align}
  E_{\mu mn}^{(p)}
  = \f{n!}{\p{n-p}!}
  \sum_{\ell=0}^{m-p-1} D_{\mu,m-p,n-p}^{(\ell)} \p{2\ell+F_{\mu np}}
  \sum_{\p{\v k,p,\ell}} \prod_{j=1}^{p-1} \p{2k_{p-j}-j+F_{\mu np}}.
  \label{eq:E_mn_p_sum}
\end{align}
We now define
\begin{align}
  f_{\mu np\ell}\p{k,q} \equiv \p{\ell-k+q} \p{\ell+k-q+F_{\mu np}},
\end{align}
and evaluate sums successively over $k_{p-1},k_{p-2},\cdots,k_2,k_1$
respectively from $k_{p-2},k_{p-3},\cdots,k_1,0$ to $\ell$, finding
\begin{align}
  \sum_{\p{\v k,p,\ell}} \prod_{j=1}^{p-1} \p{2k_{p-j}-j+F_{\mu np}}
  &= \sum_{\p{\v k;p-1;\ell}}
  \prod_{j=2}^{p-1} \p{2k_{p-j}-j+F_{\mu np}}
  f_{\mu n\ell}\p{k_{p-2},1} \\
  &= \f12 \sum_{\p{\v k,p-2,\ell}}
  \prod_{j=3}^{p-1} \p{2k_{p-j}-j+F_{\mu np}}
  f_{\mu np\ell}\p{k_{p-3},1} f_{\mu np\ell}\p{k_{p-3},2} \\
  &= \f1{r!} \sum_{\p{\v k,p-r,\ell}}
  \prod_{j=1+r}^{p-1} \p{2k_{p-j}-j+F_{\mu np}}
  \prod_{q=1}^r f_{\mu np\ell}\p{k_{p-1-r},q} \\
  &= \f1{\p{p-1}!} \prod_{q=1}^{p-1} f_{\mu np\ell}\p{0,q} \\
  &= { \ell + p - 1 \choose p - 1 }
  \prod_{q=1}^{p-1} \p{\ell-q+F_{\mu np}}.
\end{align}
Substitution of this result together with $D_{\mu,m-p,n-p}^{(\ell)}$
as given in using \eqref{eq:D_mn_k} into $E_{\mu mn}^{(p)}$ as
expressed in \eqref{eq:E_mn_p_sum} then gives us
\begin{align}
  E_{\mu mn}^{(p)}
  = \f{n!}{\p{n-p-1}!} S_\bmu^{n-p-1} S_\mu^{m-p-1} G_{\mu mnp}
\end{align}
with
\begin{align}
  G_{\mu mnp}
  &\equiv \sum_{\ell=0}^{m-p-1} { \ell + p - 1 \choose p - 1 }
  \p{m-p-\ell} \p{\ell+m-p+F_{\mu np}}
  \p{2\ell + F_{\mu np}}
  \prod_{q=1}^{p-1} \p{\ell-q+F_{\mu np}} \\
  &= { m \choose p + 1 } \prod_{q=0}^p \p{m-p-q+F_{\mu np}}.
\end{align}
By substitution of $F_{mu np}=p-n+2\mu S_z$, we can expand
\begin{align}
  \prod_{q=0}^p \p{m-p-q+F_{\mu np}}
  = \prod_{q=0}^p \p{m-n-q+2\mu S_z}
  = \sum_{q=0}^{p+1} \p{2\mu S_z}^q e_{p+1-q}\p{m-n-\Z_{p+1}},
\end{align}
where $m-n-\Z_{p+1}=\set{m-n-j:j\in\Z_{p+1}}$ and $e_k\p{\S}$ is the
elementary symmetric polynomial of degree $k$ in elements of $\S$,
i.e.~the sum of all products of $k$ distinct elements chosen from
$\S$.  Putting everything together, we have that
\begin{align}
  E_{\mu mn}^{(p)}
  = { m \choose p + 1 } { n \choose p + 1 } \p{p+1}!
  S_\bmu^{n-p-1} S_\mu^{m-p-1}
  \sum_{q=0}^{p+1} \p{2\mu}^q e_{p+1-q}\p{m-n-\Z_{p+1}} S_z^q,
\end{align}
in terms of which
\begin{align}
  \sp{S_\mu^m, S_\bmu^n}_-
  = mn S_\bmu^{n-1} S_\mu^{m-1} \p{m-n+2\mu S_z}
  + \sum_{p=1}^{\min\set{m,n}-1} E_{\mu mn}^{(p)}.
\end{align}

\newpage
\section{Decoherence of Heisenberg spin operators}
\label{sec:decoherence}

The decoherence operator for uncorrelated single-spin decay at a
uniform rate is
\begin{align}
  \D\p{\O}
  \equiv \sum_j\p{\sigma_j^+\O\sigma_j^-
    - \f12\sp{\sigma_j^+\sigma_j^-,\O}_+},
\end{align}
where
\begin{align}
  \sum_j \f12\sp{\sigma_j^+\sigma_j^-,\O}_+
  = \f12\sp{S+S_z,\O}_+
  = S\O + \f12\sp{S_z,\O}_+
  = \O\p{S+S_z} + \f12\sp{S_z,\O}_-,
\end{align}
so
\begin{align}
  \D\p{\O}
  = \sum_j \sigma_j^+\O\sigma_j^- - \O\p{S + S_z} - \f12 \sp{S_z,\O}_-.
\end{align}
We are interested in the effect of this decoherence on the dynamics of
collective spin operators, all of which are determined by operators of
the form $S_+^\ell S_-^m S_z^n$.  We thus expand
\begin{align}
  \D\p{S_+^\ell S_-^m S_z^n}
  = \sum_j \sigma_j^+ S_+^\ell S_-^m S_z^n \sigma_j^-
  - S_+^\ell S_-^m S_z^n \p{S + S_z}
  - \f12 \sp{S_z, S_+^\ell S_-^m S_z^n}_-.
  \label{eq:D_z+-}
\end{align}
The last term in \eqref{eq:D_z+-} is straightforward to simplify using
\eqref{eq:push_z_mu_nu}:
\begin{align}
  \f12 \sp{S_z, S_+^\ell S_-^m S_z^n}_-
  = \f12 \sp{S_z, S_+^\ell S_-^m}_- S_z^n
  = \f12 \p{\ell-m} S_+^\ell S_-^m S_z^n,
\end{align}
while the first term in \eqref{eq:D_z+-} can be written in terms of
collective spin operators if we use
\eqref{eq:comm_z_mu}-\eqref{eq:comm_mu_nu} to push the jump operators
together:
\begin{align}
  \sum_j \sigma_j^+ S_+^\ell S_-^m S_z^n \sigma_j^-
  = \sum_j S_+^\ell \sigma_j^+ \sigma_j^- S_-^m \p{S_z-1}^n
  = S_+^\ell \p{S + S_z} S_-^m
  \sum_{k=0}^n \p{-1}^{n-k} { n \choose k } S_z^k.
\end{align}
Finally, we need to push the middle $S_z$ to the right, which we can
do using \eqref{eq:push_z_mu}:
\begin{align}
  \sum_j \sigma_j^+ S_+^\ell S_-^m S_z^n \sigma_j^-
  = S_+^\ell S_-^m \p{S - m + S_z}
  \sum_{k=0}^n \p{-1}^{n-k} { n \choose k } S_z^k.
\end{align}
Altogether, we have that
\begin{align}
  \D\p{S_+^\ell S_-^m S_z^n}
  &= S_+^\ell S_-^m \sp{\p{S - m + S_z} \sum_{k=0}^n
    \p{-1}^{n-k} { n \choose k } S_z^k
    - \p{S + S_z + \f12\sp{\ell-m}} S_z^n} \\
  &= S_+^\ell S_-^m \sp{\p{S - m + S_z} \sum_{k=0}^{n-1}
    \p{-1}^{n-k} { n \choose k } S_z^k - \f12 \p{\ell+m} S_z^n}.
\end{align}
